The \kepler Smear Campaign I: An Asteroseismic Catalogue of Bright Red Giants

### 2018-11-11 paper/ms.tex
typos

\subsubsection{Chemical Compositions}
\label{chemical}
The chemical composition for each star was measured in the $\alpha$ (Mg, Ti, Si, Ca), odd-Z (Al, V) and Fe-peak (Fe, Ni) elemental families in a differential way with respect to Arcturus. The chemical composition for the neutron capture elements are shown in Fig.~\ref{fig:ncap}, and are derived not differentially with respect to Arcturus. The elemental abundance ratios were measured in order to assess the Galactic populations to which these stars belong. The first thing to note is that the metallicities, which are tabulated in Table~\ref{stellar_props}, are too high (with $-0.51<$~[M/H]~$<$ +0.14~dex) to belong to the Galactic halo, whose peak metallicity is around $\sim -1.50$ \cite[e.g.][]{Chiba2000}. Furthermore, the distance distribution, noted in Table~\ref{all_stars}, indicates that all stars are located within a few~kpc of the Sun and are not apart of the Galactic bulge. Thus, these stars are drawn from only the Galactic thick and thin disks. We provide a detailed chemical abundance analysis below to support this claim.\\

>>>>

\subsubsection{Chemical Compositions}
\label{chemical}
The chemical composition for each star was measured in the $\alpha$ (Mg, Ti, Si, Ca), odd-Z (Al, V) and Fe-peak (Fe, Ni) elemental families in a differential way with respect to Arcturus. The chemical composition for the neutron capture elements are shown in Fig.~\ref{fig:ncap}, and are derived in absolute terms and not differentially with respect to Arcturus. The elemental abundance ratios were measured in order to assess the Galactic populations to which these stars belong. The first thing to note is that the metallicities, which are tabulated in Table~\ref{stellar_props}, are too high (with $-0.51<$~[M/H]~$<$ +0.14~dex) to belong to the Galactic halo, whose peak metallicity is around $\sim -1.50$ \cite[e.g.][]{Chiba2000}. Furthermore, the distance distribution, noted in Table~\ref{all_stars}, indicates that all stars are located within a few~kpc of the Sun and are not apart of the Galactic bulge. Thus, these stars are drawn from only the Galactic thick and thin disks. We provide a detailed chemical abundance analysis below to support this claim.\\
